The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-28 paper/ms.tex
Coments about mu in the off-center

For the central and homogeneous source distributions we find that the
level of isotropy angular dependency represented by $\mu$ doesn't show
a considerable variation in particular the observer would infer
luminosities  different from the isotropical value only at levels $<
3\%$. This values were obtained for a run with $V_{\rm max}=XX$ and
$\tau_{\rm H}=XXX$ and $N_{\gamma}=10^{6}$ photons.

%%%%%%%

>>>>

For the central and homogeneous source distributions we find that the
level of isotropy angular dependency represented by $\mu$ doesn't show
a considerable variation in particular the observer would infer
luminosities  different from the isotropical value only at levels $<
3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
10^{7}$ and $N_{\gamma}=10^{5}$ photons.

For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
 $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
$\bigtriangleup\mu\leq 15\%$.
%%%%%%%
